Figure 2 and figure 2 supplementary material

### 2022-04-29 Figures/Figure2.Rmd
minor fix

```{r}
corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
corrplots$Macrophages <- summary_corr$Macrophages + rremove("y.text")
corrplots$Neutrophils <- summary_corr$Neutrophils + rremove("y.text")
summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")

>>>>

```{r}
corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
